---
title: "An Aplication to SAE HB ME under Beta Distribution On Sample Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SAE HB with Measurement Error under Beta Distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## case 1: Auxiliary variables only contains variable with error in aux variable

## STEP 1 : Load Package and Load Data Set
```{r setup}
library(saeHB.ME.beta)
data("dataHBMEbeta")
```

## STEP 2 : Fitting HB Model

```{r}
example <- meHBbeta(Y~x1+x2, var.x = c("v.x1","v.x2"),
                   iter.update = 3, iter.mcmc = 10000,
                   thin = 3, burn.in = 1000, data = dataHBMEbeta)
```

## STEP 3 : Ekstract Mean Estimation

### Small Area Mean Estimation

```{r}
example$Est
```

### Coefficient Estimation

```{r}
example$coefficient
```

### Random Effect Variance Estimation

```{r}
example$refvar
```

### Extract MSE

```{r}
MSE_HBMEbeta=example$Est$sd^2
```

### Extract RSE

```{r}
RSE_HBMEbeta=sqrt(MSE_HBMEbeta)/example$Est$mean*100
```

## You can compare with Direct Estimation

### Extract Direct  Estimation

```{r}
Y_direct=dataHBMEbeta[,1]
MSE_direct=dataHBMEbeta[,6]
RSE_direct=sqrt(MSE_direct)/Y_direct*100
```

### Comparing Y

```{r}
Y_HBMEbeta=example$Est$mean
Y=as.data.frame(cbind(Y_direct,Y_HBMEbeta))
summary(Y)
boxplot(Y,col=topo.colors(2))
```

### Comparing Mean Squared  Error (MSE)

```{r}
MSE=as.data.frame(cbind(MSE_direct,MSE_HBMEbeta))
summary(MSE)
```

### Comparing Relative Standard  Error (RSE) 

```{r}
RSE=as.data.frame(cbind(RSE_direct,RSE_HBMEbeta))
summary(RSE)
```
